### 2023-11-18 ms.qmd
Updates

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)

@@

# Bayesian model guichenoti
  guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)
# R2
bayes_R2(mod)

>>>>

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)

@@

# Bayesian model guichenoti
  guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(guich_mod)
  plot(guich_mod)
# R2
bayes_R2(deli_mod)
bayes_R2(guich_mod)
